Is multi-family housing allowed, either by right or special permit (including through overlays or cluster zoning)?                             &      3\% &         0\% \\
Are apartments above commercial (mixed use) allowed in any district?                                                                           &      0\% &         0\% \\
Is multi-family housing listed as allowed through conversion (of either single family houses or non residential buildings)?                    &      0\% &         0\% \\
Are attached single family houses (townhouses, 3+ units) listed as an allowed use (by right or special permit)?                                &      0\% &         6\% \\
Does zoning include any provisions for housing that is restricted by age?                                                                      &      0\% &         0\% \\
Are accessory or in-law apartments allowed (by right or special permit) in any district?                                                       &      3\% &         3\% \\
Is cluster development, planned unit development, open space residential design, or another type of flexible zoning allowed by right?          &      0\% &         3\% \\
Is cluster development, planned unit development, open space residential design, or another type of flexible zoning allowed by special permit? &      3\% &         3\% \\
Does the zoning bylaw/ordinance include any mandates or incentives for development of affordable units?                                        &      0\% &         0\% \\
Is there a town-wide annual or biannual cap on residential permits issued, and/or is project phasing required?                                 &      0\% &         0\% \\
Are there restrictions on counting wetlands, sloped land or easements in lot size calculations?                                                &      0\% &         0\% \\
\midrule
Cumulative Average                                                                                                                             &      0\% &         1\% \\
\bottomrule