Is multi-family housing allowed, either by right or special permit (including through overlays or cluster zoning)?                             &  0.00 &  100\% \\
Are apartments above commercial (mixed use) allowed in any district?                                                                           &  0.07 &   96\% \\
Is multi-family housing listed as allowed through conversion (of either single family houses or non residential buildings)?                    &  0.08 &   96\% \\
Are attached single family houses (townhouses, 3+ units) listed as an allowed use (by right or special permit)?                                &  0.30 &   90\% \\
Does zoning include any provisions for housing that is restricted by age?                                                                      &  0.14 &   96\% \\
Are accessory or in-law apartments allowed (by right or special permit) in any district?                                                       &  0.09 &   96\% \\
Is cluster development, planned unit development, open space residential design, or another type of flexible zoning allowed by right?          &  0.00 &  100\% \\
Is cluster development, planned unit development, open space residential design, or another type of flexible zoning allowed by special permit? &  0.00 &  100\% \\
Does the zoning bylaw/ordinance include any mandates or incentives for development of affordable units?                                        &  0.00 &  100\% \\
Is there a town-wide annual or biannual cap on residential permits issued, and/or is project phasing required?                                 &  0.33 &   90\% \\
Are there restrictions on counting wetlands, sloped land or easements in lot size calculations?                                                &  0.14 &   96\% \\
\midrule
Cumulative Average                                                                                                                             &  0.11 &   96\% \\
Cumulative Median                                                                                                                              &  0.09 &   96\% \\
\bottomrule